Tempo Analysis: The Sound of Teaching Music 1

### 2020-11-24 script/R/analysis/ioi.Rmd
correct some comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ggpaired(ioi_art_ch_plot, cond1 = "teaching", cond2 = "performing", color = "condition", legend = "none", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "jco", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed", ) +
  theme(legend.position = "none")
```

@@

ggpaired(ioi_dyn_ch_plot, cond1 = "teaching", cond2 = "performing", color = "condition", legend = "none", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "jco", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed", ) +
  theme(legend.position = "none")
```

@@

```{r ioi_dyn_trial_all_line, echo = FALSE}
ggline(ioi_dyn_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "jco", xlab = "Trial", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  scale_x_continuous(breaks=seq(1,8,1)) +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed") +
  theme(legend.position = "bottom")
```
# Sequence plot
## Articulation{#sequence_art}
```{r seq-art, fig.width = 10, fig.height = 2, echo = FALSE}
# For each individual
ioi_art_seq <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Interval)]

>>>>

ggpaired(ioi_art_ch_plot, cond1 = "teaching", cond2 = "performing", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "jco", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed", ) +
  theme(legend.position = "none")
```

@@

ggpaired(ioi_dyn_ch_plot, cond1 = "teaching", cond2 = "performing", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "jco", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed", ) +
  theme(legend.position = "none")
```

@@

```{r ioi-dyn-trial-all-line, echo = FALSE}
ggline(ioi_dyn_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "jco", xlab = "Trial", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  scale_x_continuous(breaks=seq(1,8,1)) +
  theme_pubr(base_size = 20, base_family = "Helvetica Neue LT Std 57 Condensed") +
  theme(legend.position = "bottom")
```
# Sequence plot
## Articulation{#sequence_art}
```{r seq-art, fig.width = 10, fig.height = 2, echo = FALSE}
# For each individual
ioi_art_seq <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Interval)]
